Legends for supplementary material

### 2019-03-08 Manuscript/Figures/figure_legends.Rmd
updated legends with balanced accuracy

**Figure 4. Barplots comparing model performance for each predictor type.** Model performances were evaluated using F1-score and MCC for each of the 4 resampling techniques, across both the GM12878 (A) and K562 (B) cell lines. The results presented are for models applied to 10 kb resolution data.

>>>>

**Figure 4. Barplots comparing model performance for each predictor type.** Model performances were evaluated using F1-score, MCC, and balanced accuracy for each of the 4 resampling techniques, across both the GM12878 (A) and K562 (B) cell lines. The results presented are for models applied to 10 kb resolution data.

### 2019-03-08 Manuscript/Supplementary/supplementary_legends.Rmd
updated legends with balanced accuracy

**Supplementary Figrue 4. Barplots comparing model performance for each predictor type across 25 kb, 50 kb, and 100 kb data resolutions** Model performances were evaluated using F1-scores and MCCs for each of the 4 resampling techniques, across both the GM12878 (A-C) and K562 (D-F) cell lines. Missing bars indicate that the model was unable to correctly predict any genomic regions that overlapped with flanked TAD boundaries in the test data, resulting in zero true positives. Bars that appear in the opposite direction (for MCC) indicate a negative correlation between the observed and predicted binary classifications of flanked TAD boundaries.

>>>>

**Supplementary Figrue 4. Barplots comparing model performance for each predictor type across 25 kb, 50 kb, and 100 kb data resolutions** Model performances were evaluated using F1-scores, MCCs, and balanced accuracies for each of the 4 resampling techniques, across both the GM12878 (A-C) and K562 (D-F) cell lines. Missing bars indicate that the model was unable to correctly predict any genomic regions that overlapped with flanked TAD boundaries in the test data, resulting in zero true positives. Bars that appear in the opposite direction (for MCC) indicate a negative correlation between the observed and predicted binary classifications of flanked TAD boundaries.
